No Evidence of Bias in Arrests Made by the Toronto Police Service

### 2024-01-23 outputs/paper/paper.qmd
Added Thanks
- Added thanks to github link

---
title: "No Evidence of Bias in Arrests Made by the Toronto Police Service"
author: "Aviral Bhardwaj"
abstract: The ethnic identity of citizens arrested by the police has consistently been a topic of discussion, often highlighting the pronounced skewness of certain ethnic identities. This paper seeks to analyze data from the Toronto Open Data Portal to investigate whether there is any bias in arrests made by the Toronto Police Service between 2020 and 2021, while accounting for factors such as age, booked after arrest, and search on arrest. While the population distribution of various ethnic identities varies significantly, it was found that ..... Further analysis can provide valuable insights for policymakers, law enforcement agencies, and community advocates in fostering a more equitable society while emphasizing the importance of promoting transparency and accountability in policing.
date: today
date-format: long
number-sections: true
format: pdf
toc: true
bibliography: references.bib
---

>>>>

---
title: "No Evidence of Bias in Arrests Made by the Toronto Police Service"
author: "Aviral Bhardwaj"
abstract: The ethnic identity of citizens arrested by the police has consistently been a topic of discussion, often highlighting the pronounced skewness of certain ethnic identities. This paper seeks to analyze data from the Toronto Open Data Portal to investigate whether there is any bias in arrests made by the Toronto Police Service between 2020 and 2021, while accounting for factors such as age, booked after arrest, and search on arrest. While the population distribution of various ethnic identities varies significantly, it was found that ..... Further analysis can provide valuable insights for policymakers, law enforcement agencies, and community advocates in fostering a more equitable society while emphasizing the importance of promoting transparency and accountability in policing.
date: today
date-format: long
number-sections: true
format: pdf
toc: true
thanks: "Code and data supporting this analysis is available at: https://github.com/Aviral-03/Ethnic-Identity-Arrests-Toronto"
bibliography: references.bib
---
